A secondary screen architecture to accurately capture TV viewer interactions for content personalization in TV environments

### 2014-05-02 src/paper.tex
WIP: Architecture

\usepackage{cite}

@@

Considering the interactions of millions of viewers, the captured data can provide valuable information~\cite{Teixeira2010}. For example, the content producers can obtain the user ratings given to TV programs, amount of viewers and user profiles. One important application that makes use of viewers interaction is content personalization. Content providers can infer user profiles from viewers' interactions in order to deliver personalized content.

@@

This architecture consists of a secondary screen device (which might be implemented in personal devices such as smartphones and tablets) a set-top box (STB) with return channel, and a content provider (which is responsible for providing the interactive applications and for storing the data that was captured from viewers).

The secondary screen is used to identify the users that are present in the environment. That is, the viewer can authenticate to the local set-top box by using a transparent authentication mechanism. Thus, every time a viewer is nearby the STB using a a TV application with its

@@

@@

>>>>

\usepackage{cite}
\usepackage{graphicx}

@@

Considering the interactions of millions of viewers, the captured data can provide valuable information~\cite{Teixeira2010}. For example, the content providers (CP) can obtain the user ratings given to TV programs, amount of viewers and user profiles. One important application that makes use of viewers interaction is content personalization. Content providers can infer user profiles from viewers' interactions in order to deliver personalized content.

@@

This architecture consists of secondary screen devices (which might be implemented in personal devices such as smartphones and tablets) a set-top box (STB) with return channel, and a CP (which is responsible for providing the interactive applications and for storing the data that is captured from viewers).

Initially, the CP must provide an infrastructure for viewers and the STB so that they can be authenticated to use the application services. In addition, the infrastructure must also provide data storage capabilities to store the interaction data captured from viewers. Then the STB must be authenticated in the application hosted on the CP infrastructure. Once the STB is authenticated, the viewers in the TV environment must also authenticate in the application service and register the STB in their accounts. As a result, the viewer can use their personal device as a secondary screen for that STB.

Figure~\ref{fig_architecture} Green arrows represent data flowing from the viewer to the CP infrastructure, while blue arrows represent the flow from CP to viewer. The black arrows represent data flow inside the CP infrastructure.

The secondary screen device must be used in conjunction with the STB to identify the users that are present in the environment and update context information. In the first place, the STB

That is, the viewer can authenticate to the local set-top box by using a transparent authentication mechanism. Thus, every time a viewer is nearby the STB using a a TV application with its

@@

\begin{figure}[!t]
	\centering
	\includegraphics[width=3.5in]{img/architecture.pdf}
	\caption{Architecture to capture viewers insteractions. }
	\label{fig_architecture}
\end{figure}

@@

Since applications in the TV domain have potential to deal with millions of users at the same time, it is interesting that this infrastructure has the ability to handle a growing amount of data~\cite{Lee2010}.
